---
title: "Academic promotion information"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Current level of appointment:
The level applying for:

Performance expectations (as defined by your university):

Evidence requirements:

## Research

## Teaching

The teaching section will allow you to collect the following data:

- Student emails that are evidence of good teaching
- HDRs and Honours students and completions

### Email gathering
First, you'll need to download the PDF file of every email you think is relevant, and keep it in a folder.

Then, use the following to parse all emails and obtain a RDS file in the same directory. The function will also return you the file in-memory.

```{r eval=FALSE, include=FALSE}
emails <- parsePDFEmails("Some/Folder/Path/Here")
```



### Storing Student info

This will create (or update) a CSV file, in whichever path you want, to add the students you are working with.

When you create a student, you need to add all of the information, as follows:

```{r eval=FALSE, include=FALSE}
# Use this function to add or edit a student data to a CSV file stored where you choose
storeStudents("Jane", "Shepard", "Honours", "Computer Science", "Normandy SR1", "March/2020", "November/2020", FALSE, "Fight the Reapers", "Dr Somebody", "Dr Another Person", "Path/To/Folder", "fileName.csv")

```

But to update, you can change only some records:

```{r eval=FALSE, include=FALSE}
# Use this function to add or edit a student data to a CSV file stored where you choose
storeStudents("Jane", "Shepard", completed = TRUE, csvFilePath =  "Path/To/Folder", csvFileName = "fileName.csv")

```

In both cases, the function will return the file in-memory, if you want to further explore it.



## Engagement

Contributors: Belinda Fabian & Ly Tong

This section includes suggestions for engagement activities that could be included in academic promotion applications. These examples are indicative only and do not provide a list of expectations. Engagement is interpreted in a broad sense to include discipline, industry, government and community engagement. 

Engagement with industry

- Partnerships with organisations: for profit, not-for-profit, volunteering
- Consulting projects -> could list value of projects, reports completed
- Participation in project development programs e.g. CSIRO On Prime
- Patents
- Service on industry boards and/or committees at the local, state or national level

Engagement with government

- Policy development -> changes resulting from your work
- Advocacy programs e.g. Science Meets Parliament 
- Service with government bodies 

Engagement with public 

- Public presentations - list of locations
- Blogging (own blog or collaborative) --> stats available from blog backend e.g. views, visitors, followers
- Twitter --> number of followers from profile, Twitter analytics https://analytics.twitter.com shows impressions, engagament rate, likes, retweets, replies (only allows viewing of the last 90 days of data)
- Community programs e.g. National Science Week, 
- Media appearances e.g. appearances on TV, radio, web
- Writing for general audience e.g. The Conversation, university news platforms (e.g. The Lighthouse)
- Public works e.g. art installations, consulting on museum exhibit
- Service on community boards and/or committees at the local, state or national level

Engagement with professional community

- Contributions to community support websites e.g. Stack Overflow
- Data science competitions e.g. Kaggle
- Community engagement projects e.g. citizen science
- Community development e.g. meetup groups, RLadies, rOpenSci, hackathons
- Creation of software packages/tools for open use

Engagement with schools

- curriculum development e.g. STEM at School 
- interactions with school students e.g. Skype a Scientist (discussing science with students)
- supervising students e.g. work experience placements, mentoring projects
- University events e.g. Open Day

Contributions to enhancing the employability of graduates

- establishing student links with industry/professional societies
- participating in professional practice teaching e.g. teamwork, communication, problem solving, grant writing

Engagement/leadership within one’s profession or discipline

- Professional society membership & activity
- Membership of professional or foundation boards/councils
- Peer review (IF NOT INCLUDED IN RESEARCH SECTION) -> journal article review, ARC college of experts, grant review panels

## Leadership
- University committee (e.g. department, faculty, university-level) - list how many events/meetings you have in a year
- Board membership - list position, length of service
- Conference organisation - list your role (e.g. scientific committee, symposium chair), scale of conference (e.g number of attendees, funding, international/local)
- Leading projects and initiatives (e.g. sustainability, diversity inclusion initiatives)
- Event organisation (e.g. writing retreat)
- Training events (e.g. university management course) - list the course, completion date
- Leadership roles in external professional or industry associations
- Mentoring - list how many mentees you have, length of relationship, where they are working now

