---
title: "Promotion information"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Current level of appointment:
The level applying for:

Performance expectations (as defined by your university):

Evidence requirements:

## Research

## Teaching

The teaching section will allow you to collect the following data:

- Student emails that are evidence of good teaching
- HDRs and Honours students and completions

### Email gathering
First, you'll need to download the PDF file of every email you think is relevant, and keep it in a folder. Then, you can do the following to obtain a CSV file with the parsed data:



### Storing Student info

This will create (or update) a CSV file, in whichever path you want, to add the students you are working with.

When you create a student, you need to add all of the information, as follows:

```{r eval=FALSE, include=FALSE}
# Use this function to add or edit a student data to a CSV file stored where you choose
storeStudents("Jane", "Shepard", "Honours", "Computer Science", "Normandy SR1", "March/2020", "November/2020", FALSE, "Fight the Reapers", "Dr Somebody", "Dr Another Person", "Path/To/Folder", "fileName.csv")

```

But to update, you can change only some records:

```{r eval=FALSE, include=FALSE}
# Use this function to add or edit a student data to a CSV file stored where you choose
storeStudents("Jane", "Shepard", completed = TRUE, csvFilePath =  "Path/To/Folder", csvFileName = "fileName.csv")

```

In both cases, the function will return the file in-memory, if you want to further explore it.



## Engagement

## Leadership